\documentclass[12pt]{article}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{float}
\theoremstyle{plain}     %------- 'regular' theorem types
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{example}[thm]{Example}
\newtheorem{exer}[thm]{Exercise}
\newtheorem{define}[thm]{Definition}
\usepackage[top=2cm, left=2cm, right=2cm]{geometry} 
\usepackage{parskip}
\setlength{\parindent}{0in}
\usepackage{floatflt}
\usepackage{multicol}
\usepackage{tabu}
\usepackage[hidelinks]{hyperref}
\hypersetup{
	urlcolor=blue}

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\large
%subject
City Semester  \hspace{7cm} Name:\makebox[6cm]{\hrulefill}
\\
%specific topic
Rents\\
\normalsize 
\emph{Complete all work on a separate sheet of paper with exercises clearly labeled and all reasoning and work given.}\\[.5cm]
%\emph{Show all work for full credit.}
\begin{enumerate}
	\item First let us examine the relationship between rents and different measures of income.
		\begin{enumerate}
			\item Start by researching and summarizing the difference between household income and family income. How are they different? Explain why one is typically larger than the other.
			\item Generate a scatterplot to look at the relationship between income and monthly rent. Make 1-2 observations about the plot.
			\item Give the equation of the least squares regression line and use it to predict the rents if median income next year is \$57,000.
			\item How confident are you in the model? Explain using residuals, $r^2$ value, and other observations.
		\end{enumerate}
	\item Now let us look at the relationship between rents and GDP measured in billions.
		\begin{enumerate}
			\item Start by researching roughly how GDP is calculated. What does it represent? How does it accurately or inaccurately convey the economic strength of a region?
			\item Generate a scatterplot to examine the relationship between monthly rents and GDP. Make 1-2 observations about the plot.
			\item Give the equation of the least squares regression line and use it to predict the rents if the GDP of NY next year is \$1350 billion.
			\item How confident are you in the model? Explain using residuals, $r^2$ value, and other observations.
		\end{enumerate}
	\item Conduct any other research (15-20 minutes) you may want to bring to the analysis and give a short paragraph summary of your thoughts about rents.
\end{enumerate}
	
\end{document} 